\input{title.tex}

### 2022-06-11 docs/papers/01_manuscript/03_results.tex
fix(discussion.tex): fix grammar and structure according to Cumming's comments
BREAKING CHANGE:

\begin{figure*}[!tb]
    \centering
    \includegraphics[width=32pc]{outputs/fig3.pdf}
    \caption{
        Regulating differences for provinces in the YRB.
        Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model, in the decade after the institutional shift.
        The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
        The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
    }
    \label{regulating}
\end{figure*}

>>>>

\begin{figure*}[!tb]
    \centering
    \includegraphics[width=32pc]{outputs/fig3.pdf}
    \caption{
        Regulating differences for provinces in the YRB.
        Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
        The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
        The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
    }
    \label{regulating}
\end{figure*}

### 2022-06-11 docs/papers/01_manuscript/04_discussion.tex
fix(discussion.tex): fix grammar and structure according to Cumming's comments
BREAKING CHANGE:

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it.
The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic YRB's water use if no effect is present \cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
Increased water use aligns with concerns about frequently scrambling for water that were voiced in some provinces during this period \cite{mao2000}.
On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.

% 我们认为制度结构的变化是被长期忽略的重要因素
We proposed that for these institutional shifts' divergent outcomes regarding water use, the key factors long ignored can be institutional structure changes.
The structural building blocks we depicted in Figure~\ref{structure}, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}, and here twice reframed by the institutional shifts.
Before the 98-UBR, the SES structure (i.e., fragment ecological units are linked to separate social actors) is more likely to be mismatched because isolated actors generally struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, institutional alignments since the 98-UBR improved YRCC's authority in water use regulation to match the YRB in scale, thus leading to social-ecological fit and good outcomes -a ``scale-matched'' example \cite{cumming2020a,wang2019d}.
Despite other reasons for the non-ideal effect of the 87-WAS being widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), few radical improvements in the 98-UBR suggest an over-attention paid to non-structural impacts.

% \subsection{Linking structures with ISs outcomes}
\label{discussion-2}
% discussion-2: 机制解释
Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
Therefore, we theoretically abstracted the SES structures and analyzed how different structures shape different outcomes with provincial heterogeneity.

Thus, our model suggests that a unified scale-matched institution is indispensable for sustainable water use.

% The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022}, which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
Our above theoretical discussion also aligns with the evolution of the institutions in the YRB.
When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
Furthermore, those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.

\subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
% \subsection{Limitation, insights and implications}
\label{discussion-3}
% discussion-3: 启示、未来的展望

We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides a unique case for two main reasons:
(1) The top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
(2) Since few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the structural changes of SESs.

In complex coupled human-nature systems, however, our approach also has inevitable limitations:
(1) The contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.
(2) When applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
However, since the analysis had agreed on the importance of the two institutional shifts of 87-WAS and 98-UBR in water governance \cite{wang2012b}, our results on their effects still provide insights for understanding water governance.

>>>>

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it.
The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic YRB's water use if no effect is present \cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.

\label{discussion-2}
% discussion-2: 87的增加
Increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000}.
Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), structural change has received limited attention.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{regulating}).
This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will maximize resource demands (interpreted in our structure-based model, see Figure~\ref{fig:model}).
Our theoretical analysis keeps in line with two facts.
(1) When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
(2) Those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.

\label{discussion-3}
On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
During this period, proportional decreased water use of provinces decoupled with their ability (reflected by current water use volume), indicating a result of regulation.
The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
Based on the structure, our model demonstrates that a unified scale-matched institution is also indispensable for sustainable water use.

We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
The YRB provides an informative case for two main reasons:
(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
(2) Since few large river basins have experienced such radical institutional shifts more than once, it provides a valuable natural experiment for understanding the impacts of structural changes in SESs on natural resources.

The structural building blocks we depicted here (Figure~\ref{structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
Institutional re-alignments since 98-UBR improved YRCC's authority and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
The comparison demonstrates again it's not easy to have a win-win situation in coupled human-nature systems \cite{hegwood2022}, which calls for an exceptional understanding of the SES structures \cite{bergsten2019, sayles2019}.

\subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
% \subsection{Limitation, insights and implications}
\label{discussion-4}
% discussion-3: 启示、未来的展望

In complex coupled human-nature systems, our approach has inevitable limitations:
First, the contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.
(2) When applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
However, since the analysis had agreed on the importance of the two institutional shifts of 87-WAS and 98-UBR in water governance \cite{wang2012b}, our results on their effects still provide insights for understanding water governance.
